Supplementary Material

### 2023-11-09 output/paper/manuscript.tex
Modified pipeline so that targets for processing results do not actually produce eg plots but only ready to use tibbles for plots and tables. Tested pipeline to create paper but I think I still have to manually reference tables and figures in manuscript.
Kept working on processing results for paper.

\begin{itemize}
\tightlist
\item
  The title should be less or equal than 300 characters. It should
  indicate the study design, the subject of the paper, information
  regarding exposures and outcomes assessed, and whether the study was
  observational or experimental.
\item
  The suggested length of the abstract is less or equal than 300 words.
\item
  The suggested length is \textless7,000 words, excluding abstract,
  references, tables, figure captions, acknowledgments, and
  Supplementary Material.

  \begin{itemize}
  \tightlist
  \item
    Concise sub-headings should be less or equal than 8 words, and they
    should be used to organize information rather than summarize the
    results.
  \item
    In-text citations with superscript numbers: outside periods and
    commas, but inside colons and semicolons.
  \end{itemize}
\end{itemize}

@@

@@

\begin{itemize}
\tightlist
\item
  Clearly define all outcomes, exposures, predictors, potential
  confounders, and effect modifiers.
\item
  Explain the rationale for treating race as an exposure, confounder,
  effect modifier, or other type of variable in analyses.
\end{itemize}

@@

@@

\begin{itemize}
\tightlist
\item
  Methods for selecting potential confounders (provide DAGs).
\item
  Describe all statistical methods with assumptions, including those
  used to control for confounding.

@@

  \begin{itemize}
  \tightlist
  \item
    Provide a clear and concise description of all findings without
    extrapolating beyond the study results.
  \item
    Do not limit results to those \emph{statistically significant} or
    that support the study hypotheses. Avoid using statistical
    significance testing as the sole or primary criterion for
    interpreting the obtained results. If significance testing or
    \emph{p}-values are used, report numeric \emph{p}-values, rounded to
    1-2 digits, for all results.
  \end{itemize}
\item
  Give unadjusted and confounder-adjusted estimates and their precision
  (e.g., \(95\%\) confidence interval). Make clear which confounders
  were adjusted for and why they were included. Include the number of
  observations for each analysis after accounting for missing data.
  Include numeric data within figures (e.g., forest plots), or provide
  tables with corresponding numeric data for all figures.

@@

@@

\begin{itemize}
\tightlist
\item
  Give the source of funding and the role of the funders for the present
  study and, if applicable, for the original study on which the present
  article is based.
\end{itemize}

>>>>

\begin{itemize}
\tightlist
\item
  Authorship must follow the ICMJE's criteria. Author names should be
  listed in ScholarOne and author contributions should be detailed in
  the cover letter (``Author A\ldots{}''). Neither names nor
  contributions should appear in the blinded manuscript. Do not include
  conflicts of interest.
\item
  The use of the word ``effect(s)'' as a proxy for ``association(s)'' is
  discouraged.
\item
  The length of the abstract must be less or equal than 200 words, and
  should be unstructured, stating the research questions, the methods
  used, and the results and conclusions of the research.
\item
  The length must be \textless4,000 words, excluding abstract,
  references, tables, figure captions, acknowledgments, and
  Supplementary Material.

  \begin{itemize}
  \tightlist
  \item
    Use the AMA format.
  \item
    In-text citations: full-sized Arabic numerals in parentheses within
    the sentence.
  \end{itemize}
\item
  Submission: SER members receive a 10\% discount on the fees per page.
  This should be requested in the cover letter. Also 20\% discount for
  Open Access charges. If uploading a single file (document, tables,
  figures, SM), designate the file as ``Main document - anonymous''.
\end{itemize}

@@

\textbf{Do not use ``Introduction'' as a heading}.

@@

\begin{itemize}
\item
  Clearly define all outcomes, exposures, predictors, potential
  confounders, and effect modifiers.
\item
  Explain the rationale for treating race as an exposure, confounder,
  effect modifier, or other type of variable in analyses.
\item
  Units (in \texttt{log}):

  \begin{itemize}
  \tightlist
  \item
    \texttt{hitrtse} in \texttt{ms}.
  \item
    EDCs in \texttt{microg/L}.
  \item
    Cortisol production and cortisone production in \texttt{ng/mL}.
  \item
    Cortisol metabolism and 11bHSD in \texttt{NA}.
  \end{itemize}
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  For RQ1 I used creatinine values from HELIX. For RQ3 the ones from the
  steroids dataset. For RQ2, I included in the model both variables.
\end{itemize}

@@

\begin{itemize}
\item
  In RQ2, I included the logarithm of the denominator in the RHS. In
  RQ3, I used the logarithm of the ratio in the RHS.
\item
  Methods for selecting potential confounders (provide DAGs).
\item
  Whenever possible, mathematical equations should be written on a
  single line. For multiplication, use a times sign.
\item
  Describe all statistical methods with assumptions, including those
  used to control for confounding.

@@

  \begin{itemize}
  \tightlist
  \item
    Provide a clear and concise description of all findings without
    extrapolating beyond the study results.
  \item
    Do not limit results to those \emph{statistically significant} or
    that support the study hypotheses. Avoid using statistical
    significance testing as the sole or primary criterion for
    interpreting the obtained results. If significance testing or
    \emph{p}-values are used, report numeric \emph{p}-values, rounded to
    1-2 digits, for all results. Use an uppercase italic letter ``P'',
    and the values should not be bolded. Indicate whether are 1- or
    2-sided.
  \end{itemize}
\item
  Give unadjusted and confounder-adjusted estimates and their precision
  (e.g., \(95\%\) confidence interval). Make clear which confounders
  were adjusted for and why they were included. Include the number of
  observations for each analysis after accounting for missing data.
  Include numeric data within figures (e.g., forest plots), or provide
  tables with corresponding numeric data for all figures.

@@

\subsubsection{What does the literature
say?}\label{what-does-the-literature-say}

\begin{itemize}
\tightlist
\item
  EDCs and neurodevelopment (ANT).
\item
  EDCs and corticosteroids.
\item
  Corticosteroids and neurodevelopment (ANT).
\end{itemize}

@@

### 2023-11-09 output/paper/si.qmd
Kept working on processing results for paper.

```{r}
source("code/dictionary.R")
source("code/data.R")
source("code/proc_res.R")
```

@@

edcs_info <- myphd::edcs_information() |>
  tidylog::select(-c(chem_id, smiles, ctd_id, exposome_explorer_id)) |>
  tidylog::mutate(
    var = janitor::make_clean_names(
      edcs_info$short_name,
      replace = c(`-` = ""),
      case = "none"
    ) |>
      tolower()
  ) |>
  tidylog::relocate(var, .after = short_name)
gt::gt(edcs_info,
       groupname_col = "class") |>
  gt::sub_values(
    values = c("NA"),
    replacement = ""
  ) |>
  gt::cols_label(
    full_name = "Compound",
    short_name = "Symbol",
    var = "Variable name",
    pubchem_cid = "PubChem CID",
    parental_compound = "Parental compound"
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  )
```

@@

viz_desc_vars(
  dat = load_dat_request()$dat,
  vars = vars_of_interest(append_to_chem = "cdesc")$chemicals,
  fct_levels = c(1, 2, 3, 4),
  is_chem = TRUE
)
```

@@

viz_desc_vars(
  dat = myphd::extract_cohort(load_steroids()$desc,
                              id_var = id_var) |>
    tidylog::mutate(
      cohort = dplyr::case_when(
        cohort == "EDE" ~ "EDEN",
        cohort == "KAN" ~ "KANC",
        cohort == "MOB" ~ "MOBA",
        cohort == "RHE" ~ "RHEA",
        .default = cohort
      )
    ),
  vars = vars_of_interest()$metabolites |>
    paste0("_cdesc"),
  fct_levels = c(1, 2, 3, 4),
  is_chem = FALSE
)
```

@@

>>>>

```{r}
source("code/dictionaries.R")
source("code/data.R")
source("code/proc_res.R")
```

@@

edcs_info <- myphd::edcs_information() |>
  tidylog::select(-c(chem_id, smiles, ctd_id, exposome_explorer_id)) |>
  tidylog::mutate(
    var = janitor::make_clean_names(
      short_name,
      replace = c(`-` = ""),
      case = "none"
    ) |>
      tolower()
  ) |>
  tidylog::relocate(var, .after = short_name)
gt::gt(edcs_info,
       groupname_col = "class") |>
  gt::sub_values(
    values = c("NA"),
    replacement = ""
  ) |>
  gt::cols_label(
    full_name = "Compound",
    short_name = "Symbol",
    var = "Variable name",
    pubchem_cid = "PubChem CID",
    parental_compound = "Parental compound"
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  )
```

@@

viz_desc_vars(
  dat = load_dat_request()$dat,
  vars = vars_of_interest(append_to_chem = "cdesc")$chemicals,
  fct_levels = c(1, 2, 3, 4),
  is_chem = TRUE
)$plot
```

@@

viz_desc_vars(
  dat = myphd::extract_cohort(load_steroids()$desc,
                              id_var = id_var) |>
    tidylog::mutate(
      cohort = dplyr::case_when(
        cohort == "EDE" ~ "EDEN",
        cohort == "KAN" ~ "KANC",
        cohort == "MOB" ~ "MOBA",
        cohort == "RHE" ~ "RHEA",
        .default = cohort
      )
    ),
  vars = vars_of_interest()$metabolites |>
    paste0("_cdesc"),
  fct_levels = c(1, 2, 3, 4),
  is_chem = FALSE
)$plot
```

@@

### Average dose-response functions for significant results

```{r}
targets::tar_load(
  dplyr::matches("marginal_gcomp_(\\d)$"),
  store = store
)
```

```{r adrfs-rq3}
#| label: fig-adrfs-rq3
#| fig-cap: Average dose-response functions for RQ3
#| fig-subcap:
#|   - "Cortisol production"
#|   - "11bHSD"
#| fig-width: 6
#| fig-height: 7
#| layout-ncol: 2

exposures_of_interest <- c(
  "cortisol production",
  "X11bHSD"
)
ret_adrfs <- lapply(
  exposures_of_interest, function(x) {
    plot_adrf(
      df_preds = marginal_gcomp_3 |>
        tidylog::filter(
          variable == x
        )
    )
  }
)
ret_adrfs[[1]]
ret_adrfs[[2]]
```
